Performance Optimization of Service Chain \\for vCPE in Small Size Network \\with OpenFlow Switch

### 2017-02-24 netsoft_paper.tex
Limit Youtube Domain

@@

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=3in]{./figures/mft_qos_rate_domain_app}
\caption{Limit the Youtube rate to a network domain.}
\label{fig:mft_qos_rate_domain_app}
\end{figure}

@@

There are a lot of people using the streaming applications nowadays and those applications always take up an amount of network’s source. We integrated with application identification to classify each flow belongs what the application is, consequently.
We choose YouTube to verify our limitation function of applications and there are 3 Hosts (Host 1, Host 2 and Host 3) in the same network domain. Then we will limit the Youtube’s bandwidth of this network domain, that is, the sum of bandwidth from Youtube of Host 1, Host 2 and Host 3.
As shown in Figure.? In the beginning without limitation, the total bandwidth of this network is about 3000 Kbps to 4000 Kbps. At \nth{8} seconds, we limited the total bandwidth from Youtube to 2048 Kbps in this network domain. Therefore, we can find out the total traffic of Youtube from this network domain is reducing immediately. Clearly, the total traffic from Youtube will not exceed the limited bandwidth (2048Kbps) since we limited the Youtube to this network domain.
When using our limitation function of application, we can guarantee the traffic of this network domain will not over the network capacity and prevent the traffic congestion in short.
